### 2019-10-11 paper/methods.tex

\begin{table}  %[!ht]
	\caption{Reactor-grade plutonium vector \cite{marka1993explosive}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (\%) \cite{de2000scenarios}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

@@

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. 
Then, the system extracted gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pu) with 
suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This can be done by set the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, protactinium was removed 
from the fuel with a certain flow rate into the external tank, 
\texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium 
extracted from the core.}, to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. The mass of the 
fissile and fertile materials needed to achieve criticality is calculated at 
the end of the cycle. Then, this mass is added to the core at the beginning of 
the cycle by a certain flow rate.

>>>>

\begin{table}  %[!ht]
	\caption{Reactor-grade plutonium vector (Mass fraction \%) \cite{marka1993explosive}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (Mass fraction \%) \cite{de2000scenarios}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

@@

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. 
Then, the system extracted gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pu) with 
suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This can be done by set the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, protactinium was removed 
from the fuel with a certain flow rate into the external tank, 
\texttt{pa-decay tank}, to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the mass flow ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
transfer rates should be connected to materials with a reprocessing scheme. 
Finally, we have to link the reprocessing schemes to depletion histories. In 
the present work, we adjusted the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation started without any injection of refueling materials (i.e. with only removing of FPs and Pa).
	\item After first depletion calculation step, we checked the total mass density of FPs and Pa in \texttt{FP-waste tank} and \texttt{pa-tank}, respectively.
	\item A simple calculation yields the amount of Th and $^{233}$U that must be added during this cycle (mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa).
	\item Dividing this mass by time and inventory of refueling material gave the corresponding feed constant.
\end{enumerate}
The cycle calculation ran iteratively until the burnup reached the desired worth.
